### 2012-03-21 docs/NewBCRobustness_paper/paper.tex
fixed paper so it compiles correctly now
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@383 36274a68-8941-4c93-80ef-affaed5139da

In \cite{DPGrobustness}, the quasi-optimal test norm was shown to induce an energy norm that is equivalent from above and below with

>>>>

In \cite{DPGrobustness}, the quasi-optimal test norm was shown to induce an energy norm that is bounded from both above and below by norms on $U$ that do not grow in magnitude with $\epsilon^{-1}$.
